Condition-Based Maintenance for Complex Systems\\ based on Current Component Status\\ and Bayesian Updating of Component Reliability

### 2016-11-24 cbm-rbd-paper.tex
first sim figure

small simulation study

@@

@@

\begin{figure}
\includegraphics[width=\textwidth]{br1sim2fig5}
\caption{***Simulation study, each repetition consists of simulating 5 subsequent operational cycles,
where failure times are earlier than expected.}
\label{fig:br1sim2fig5}
\end{figure}

>>>>

We now present a small simulation study

@@

\begin{figure}
\includegraphics[width=\textwidth]{br1sim1fig5}
\caption{***Simulation study, each repetition consists of simulating 5 subsequent operational cycles,
where failure times are simulated according to prior parameters.}
\label{fig:br1sim1fig5}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\textwidth]{br1sim2fig5}
\caption{***Simulation study, each repetition consists of simulating 5 subsequent operational cycles,
where failure times are simulated as being earlier than expected.}
\label{fig:br1sim2fig5}
\end{figure}
